\documentclass[12pt]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{cite}

\title{Integrating Nsu Calender to Google Calender.}
\author{Mohammad Mansib Newaz,1931842642}
\date{March 2019}

\begin{document}

\maketitle
The idea is to explore the possibility of integrating Nsu Semester Calendar to Google Calendar. 
General Consensus Tells us that Nsu Students Rely on Google Calendar as their scheduling platform. Nsu Semester Calendar often Consist of Key dates of Tuition Fee Clearance. Historically there were multiple Change logs to the Semester Calendar that turns into revised calendars. If the Proposed Project is plausible One can easily have automated Synced NSU calendar. As The entire Faculty as well as student rely on Gsuite Work-space for Academic Sessions. The Project Capitalizes on the Idea that a Back-end Server can Manipulate Existing Nsu published Semester Calendar and Integrate into The Collectively Used Google Calendar. 

The Route to Project Completion can be done by reaching the Following Milestone. 
1. Fetching The Semester-Calendar. 
2. Using Open Source Api to Translate it into CSV/SQL Data. 
3. Restructuring the existing Information According to Google Calender Import structure. 
4. A Script that will run and update any revision. 
 
 
 NB: This was a Personal Project I picked up to aid my learning during the semester break. Milestone 1 and 2 are already achieved and can be Obtained From The github link : 


\bibliographystyle{plain}
\bibliography{M335}

\end{document}
